\chapter{Background and/or status of the matter}

Nowadays, there are many solutions that can fit to solve our problem. Some are very expensive, and others have shortcomings. In this chapter, we will have a look at some of the most popular solutions.

\section{Smaart}

\textbf{Smaart}, acronym for \textit{System Measurement Acoustic Analysis Real-time Tool}, is a software-based solution commercialized by Rational Acoustics. It is probably the most used and well-known solution for professional acoustic analysis, used in big venues, concert halls, stadiums, touring productions, as well as in professional audio studios and speaker development laboratories.  Common uses are:

\begin{itemize}
	\item \textbf{Speaker Alignment:} When we have multiple sound sources, this software helps us find the phase and delay between them. For example, it can be used to find the time and phase alignment between a subwoofer and a full-range speaker.
	
	\item \textbf{RTA:} Real-Time Analysis, used to view live spectrograms, phase deviation, or energy in frequency bands. One example of use is identifying resonances at specific frequencies.
	
	\item \textbf{Frequency and Phase Response} used to view spectrograms, phase dviation, ...................

\begin{center}
\vspace{-2mm}
\tikzsetnextfilename{vad_fsa_basico}
\begin{tikzpicture}[node distance=30mm,on grid,auto, scale=1, bend angle=45]
	% \draw[help lines] (0,0) grid (3,2);
	every node/.style={font=\small};
	
	\node (q_init) {start};
	\node (null_init) [right=of q_init] {};
	\node[state, minimum size=15mm] (q_sil) [above right=of null_init] {silence};
	\node[state, minimum size=15mm] (q_voice) [below right=of null_init] {voice};
	\node (null_final) [above right=of q_voice] {};
	\node (q_final) [right=of null_final] {end};
	
	
	\draw[blue, dotted, very thick, ->] (q_init) edge node {} (q_sil);
	\draw[blue, dotted, very thick, ->] (q_init) edge node {} (q_voice);
	\draw[blue, dotted, very thick, ->] (q_sil) edge node {} (q_final);
	\draw[blue, dotted, very thick, ->] (q_voice) edge node {} (q_final);
	
	\path[->,every node/.style={font=\footnotesize}]
	(q_sil) edge [bend left, thick] node {$C_{S,V}$} (q_voice)
	edge [loop above, thick] node {$C_{S}$} ()
	(q_voice) edge [bend left, thick] node  {$C_{V,S}$} (q_sil)
	edge [loop above, thick] node {$C_{V}$} ()
	;
\end{tikzpicture}
\vspace{-2mm}
\end{center}